Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-07-10 tse19/main.tex
updates tables

Column ``\emph{Subject}'' indicates the name of the project, column
\begin{wraptable}{r}{5cm}
\vspace{-4mm}
\caption{Subjects with parallel test execution enabled by default.}
\label{tab:freqmodes-dynamic}
\footnotesize
\centering
\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{llcr}
\toprule
\multirow{2}{*}{\emph{Group}} & \multirow{2}{*}{\emph{Subject}} & \emph{\# of} & \multirow{2}{*}{\emph{Mode}}\\%
   & & \emph{modules} &\\%
\midrule%
Medium & \Comment{alibaba} Nacos & 1/10 & C1\\%
Long & \Comment{apache} Avro & 7/18 & C3\\%
Medium & \Comment{apache} Flink & 108/123 & FC0\\%
Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
Medium & \Comment{atmosphere} Nettosphere & 2/2 & FC0\\%
Medium & Chaos & 1/1 & C2\\%
Medium & Cache2k & 10/10 & C2\\%
Medium & \Comment{dropwizard} Metrics & 1/23 & C2\\%
Medium & \Comment{eclipse} Leshan & 11/11 & C2\\%
Medium & \Comment{facebook} Jcommon & 16/16 & FC0\\%
Long & Search Guard & 1/1 & FC0\\%
Long & \Comment{Hazelcast} Jet & 8/8 & FC0\\%
Long & Javaparser & 1/9 & C1\\%
Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
Long & Optaplanner & 1/13 & FC0\\%
Medium & \Comment{spring-data-cassandra}  Cassandra & 1/1 & C1\\%
Medium & Togglz & 1/34 & C1\\%
Long & Twilio Java & 1/1 & FC0\\%
Long & Vavr & 4/4 & C3\\%
Medium & Rultor & 1/1 & C3\\%
Medium & \Comment{problem-spring-web}  Spring Web & 4/4 & C3\\%
Medium & Zxing & 4/4 & FC0\\%
\bottomrule%
\end{tabular}
\end{wraptable}
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.
We note that, considering these projects, the modules that do not use
the configuration cited use the sequential configuration \Seq{}.
For example, eleven modules (=18-7) from Avro use sequential
configuration. It came as a surprise the observation that
no project used distinct configurations in their modules.

>>>>

Column ``\emph{Subject}'' indicates the name of the project, column
\begin{wraptable}{r}{5cm}
\vspace{-4mm}
\caption{Subjects with parallel test execution enabled by default.}
\label{tab:freqmodes-dynamic}
\footnotesize
\centering
\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{llcr}
\toprule
\multirow{2}{*}{\emph{Group}} & \multirow{2}{*}{\emph{Subject}} & \emph{\# of} & \multirow{2}{*}{\emph{Mode}}\\%
   & & \emph{modules} &\\%
\midrule%
Long & \Comment{apache} Avro & 7/18 & C3\\%
Medium & Cache2k & 10/10 & C2\\%
Medium & \Comment{spring-data-cassandra}  Cassandra & 1/1 & C1\\%
Medium & Chaos & 1/1 & C2\\%
Medium & \Comment{apache} Flink & 108/123 & FC0\\%
Long & Javaparser & 1/9 & C1\\%
Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
Medium & \Comment{facebook} Jcommon & 16/16 & FC0\\%
Long & \Comment{Hazelcast} Jet & 8/8 & FC0\\%
Medium & \Comment{eclipse} Leshan & 11/11 & C2\\%
Medium & \Comment{dropwizard} Metrics & 1/23 & C2\\%
Medium & \Comment{alibaba} Nacos & 1/10 & C1\\%
Medium & \Comment{atmosphere} Nettosphere & 2/2 & FC0\\%
Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
Long & Optaplanner & 1/13 & FC0\\%
Medium & Rultor & 1/1 & C3\\%
Long & Search Guard & 1/1 & FC0\\%
Medium & \Comment{problem-spring-web}  Spring Web & 4/4 & C3\\%
Medium & Togglz & 1/34 & C1\\%
Long & Twilio Java & 1/1 & FC0\\%
Long & Vavr & 4/4 & C3\\%
Medium & Zxing & 4/4 & FC0\\%
\bottomrule%
\end{tabular}
\end{wraptable}
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.
We note that, considering these projects, the modules that do not use
the configuration cited use the sequential configuration \Seq{}.
For example, eleven modules (=18-7) from Avro use sequential
configuration. It came as a surprise the observation that
no project used distinct configurations in their modules.
